Placeholder for article 3

### 2025-01-14 analysis/paper/paper.qmd
Improved retouched tool tables

# Solutrean table
solutrean_retouch <- solutrean_dataset %>%
    mutate(CLASS = case_when(
    CLASS == "Retouched piece" ~ "RetouchedPiece",
    CLASS == "Retouched piece fragment" ~ "RetouchedPieceFrag",
    TRUE ~ CLASS)) %>% 
  filter(CLASS %in% c("RetouchedPiece", "RetouchedPieceFrag")) %>% 
  select(RMTYPE, RETOUCHEDPIECETYPOLOGY) %>%
  filter(RETOUCHEDPIECETYPOLOGY != "") %>% 
  group_by(RMTYPE)

solutrean_retouch_tab <- solutrean_retouch %>% 
  tabyl(RETOUCHEDPIECETYPOLOGY, RMTYPE) %>% 
  adorn_totals(c("row", "col")) %>% 
  adorn_percentages("col") %>% 
  adorn_pct_formatting(2) %>% 
  adorn_ns("front")

# Proto-solutrean table
proto_retouch <- phase_dataset %>% 
  filter(CLASS %in% c("RetouchedPiece", "RetouchedPieceFrag")) %>%
  filter(Level %in% c("4E", "4E/5")) %>% 
  select(RMTYPE, RETOUCHEDPIECETYPOLOGY) %>% 
  dplyr::group_by(RMTYPE)

proto_retouch_tab <- proto_retouch %>%
  tabyl(RETOUCHEDPIECETYPOLOGY, RMTYPE) %>%
  adorn_totals(c("row", "col")) %>% 
  adorn_percentages("col") %>% 
  adorn_pct_formatting(2) %>% 
  adorn_ns("front")

# Gravettian table
gravettian_retouch <- phase_dataset %>% 
  filter(CLASS %in% c("RetouchedPiece", "RetouchedPieceFrag")) %>%
  filter(Level %in% c(6, 7)) %>% 
  select(RMTYPE, RETOUCHEDPIECETYPOLOGY) %>% 
  dplyr::group_by(RMTYPE)

gravettian_retouched_tab <- gravettian_retouch %>% 
  tabyl(RETOUCHEDPIECETYPOLOGY, RMTYPE) %>%
  adorn_totals(c("row", "col")) %>% 
  adorn_percentages("row") %>% 
  adorn_pct_formatting(2) %>% 
  adorn_ns("front")

>>>>

# Solutrean table
## Table preparation
solutrean_retouch <- solutrean_dataset |>
    mutate(CLASS = case_when(
    CLASS == "Retouched piece" ~ "RetouchedPiece",
    CLASS == "Retouched piece fragment" ~ "RetouchedPieceFrag",
    TRUE ~ CLASS)) |>
  filter(CLASS %in% c("RetouchedPiece", "RetouchedPieceFrag")) |>
  select(RMTYPE, RETOUCHEDPIECETYPOLOGY) |>
  filter(RETOUCHEDPIECETYPOLOGY != "") |>
  dplyr::mutate(RMTYPE = case_when(
    RMTYPE == "TYPE 1" ~ "T1",
    RMTYPE == "TYPE 2" ~ "T2",
    RMTYPE == "TYPE 3" ~ "T3",
    RMTYPE == "TYPE 4" ~ "T4",
    RMTYPE == "TYPE 5" ~ "T5",
    RMTYPE == "TYPE 6" ~ "T6",
    RMTYPE == "TYPE 7" ~ "T7",
    RMTYPE == "TYPE 8" ~ "T8",
    RMTYPE == "TYPE 9" ~ "T9",
    RMTYPE == "TYPE 10" ~ "T10",
    RMTYPE == "TYPE 11" ~ "T11",
    TRUE ~ RMTYPE))
## Janitor tabyl for final table with n and %
solutrean_retouch_tab <- solutrean_retouch |>
  tabyl(RETOUCHEDPIECETYPOLOGY, RMTYPE) |>
  adorn_totals(c("row", "col")) |>
  adorn_percentages("col") |>
  adorn_pct_formatting(2) |> 
  adorn_ns("front")
## Cleaning final table
solutrean_retouch_tab <- solutrean_retouch_tab |>
    dplyr::mutate(T1 = case_when( # Replace 0% values with -
    T1 == "0   (0.00%)" ~ "-",
    TRUE ~ T1)) |>
  dplyr::mutate(T2 = case_when(
    T2 == "0   (0.00%)" ~ "-",
    TRUE ~ T2)) |>
  dplyr::mutate(T5 = case_when(
    T5 == "0   (0.00%)" ~ "-",
    TRUE ~ T5)) |>
  dplyr::mutate(T6 = case_when(
    T6 == "0   (0.00%)" ~ "-",
    TRUE ~ T6)) |>
  dplyr::mutate(T7 = case_when(
    T7 == "0   (0.00%)" ~ "-",
    TRUE ~ T7)) |>
  dplyr::mutate(T8 = case_when(
    T8 == "0   (0.00%)" ~ "-",
    TRUE ~ T8)) |>
  dplyr::mutate(T11 = case_when(
    T11 == "0   (0.00%)" ~ "-",
    TRUE ~ T11)) |>
  dplyr::mutate(INDET = case_when(
    INDET == "0   (0.00%)" ~ "-",
    TRUE ~ INDET)) |>
  select(RETOUCHEDPIECETYPOLOGY, T1, T2, T5, T6, T7, T8, T11, INDET, Total) # Ordering values

# Proto-solutrean table
## Table preparation
proto_retouch <- phase_dataset |>
  filter(CLASS %in% c("RetouchedPiece", "RetouchedPieceFrag")) |>
  filter(Level %in% c("4E", "4E/5")) |>
  select(RMTYPE, RETOUCHEDPIECETYPOLOGY) |>
  dplyr::mutate(RMTYPE = case_when(
    RMTYPE == "TYPE 1" ~ "T1",
    RMTYPE == "TYPE 2" ~ "T2",
    RMTYPE == "TYPE 3" ~ "T3",
    RMTYPE == "TYPE 4" ~ "T4",
    RMTYPE == "TYPE 5" ~ "T5",
    RMTYPE == "TYPE 6" ~ "T6",
    RMTYPE == "TYPE 7" ~ "T7",
    RMTYPE == "TYPE 8" ~ "T8",
    RMTYPE == "TYPE 9" ~ "T9",
    RMTYPE == "TYPE 10" ~ "T10",
    RMTYPE == "TYPE 11" ~ "T11",
    TRUE ~ RMTYPE))
## Janitor tabyl for final table with n and %
proto_retouch_tab <- proto_retouch %>%
  tabyl(RETOUCHEDPIECETYPOLOGY, RMTYPE) %>%
  adorn_totals(c("row", "col")) %>% 
  adorn_percentages("col") %>% 
  adorn_pct_formatting(2) %>% 
  adorn_ns("front")
## Cleaning final table
proto_retouch_tab <- proto_retouch_tab |>
  dplyr::mutate(T1 = case_when( # Replace 0% values with -
    T1 == "0   (0.00%)" ~ "-",
    TRUE ~ T1)) |>
  dplyr::mutate(T2 = case_when(
    T2 == "0   (0.00%)" ~ "-",
    TRUE ~ T2)) |>
  dplyr::mutate(T3 = case_when(
    T3 == "0   (0.00%)" ~ "-",
    TRUE ~ T3)) |>
  dplyr::mutate(T4 = case_when(
    T4 == "0   (0.00%)" ~ "-",
    TRUE ~ T4)) |>
  dplyr::mutate(T5 = case_when(
    T5 == "0   (0.00%)" ~ "-",
    TRUE ~ T5)) |>
  dplyr::mutate(T6 = case_when(
    T6 == "0   (0.00%)" ~ "-",
    TRUE ~ T6)) |>
  dplyr::mutate(T7 = case_when(
    T7 == "0   (0.00%)" ~ "-",
    TRUE ~ T7)) |>
  dplyr::mutate(T8 = case_when(
    T8 == "0   (0.00%)" ~ "-",
    TRUE ~ T8)) |>
  dplyr::mutate(T9 = case_when(
    T9 == "0   (0.00%)" ~ "-",
    TRUE ~ T9)) |>
  dplyr::mutate(TL = case_when(
    TL == "0   (0.00%)" ~ "-",
    TRUE ~ TL)) |>
  dplyr::mutate(INDET = case_when(
    INDET == "0   (0.00%)" ~ "-",
    TRUE ~ INDET))

# Gravettian table
## Table preparation
gravettian_retouch <- phase_dataset %>% 
  filter(CLASS %in% c("RetouchedPiece", "RetouchedPieceFrag")) %>%
  filter(Level %in% c(6, 7)) %>% 
  select(RMTYPE, RETOUCHEDPIECETYPOLOGY) %>% 
  dplyr::group_by(RMTYPE) |>
  dplyr::mutate(RMTYPE = case_when(
    RMTYPE == "TYPE 1" ~ "T1",
    RMTYPE == "TYPE 2" ~ "T2",
    RMTYPE == "TYPE 3" ~ "T3",
    RMTYPE == "TYPE 4" ~ "T4",
    RMTYPE == "TYPE 5" ~ "T5",
    RMTYPE == "TYPE 6" ~ "T6",
    RMTYPE == "TYPE 7" ~ "T7",
    RMTYPE == "TYPE 8" ~ "T8",
    RMTYPE == "TYPE 9" ~ "T9",
    RMTYPE == "TYPE 10" ~ "T10",
    TRUE ~ RMTYPE))
## Janitor tabyl for final table with n and %
gravettian_retouched_tab <- gravettian_retouch %>% 
  tabyl(RETOUCHEDPIECETYPOLOGY, RMTYPE) %>%
  adorn_totals(c("row", "col")) %>% 
  adorn_percentages("col") %>% 
  adorn_pct_formatting(2) %>% 
  adorn_ns("front")
## Cleaning final table
gravettian_retouched_tab <- gravettian_retouched_tab |>
  dplyr::mutate(T1 = case_when( # Replace 0% values with -
    T1 == "0   (0.00%)" ~ "-",
    TRUE ~ T1)) |>
  dplyr::mutate(T2 = case_when(
    T2 == "0   (0.00%)" ~ "-",
    TRUE ~ T2)) |>
  dplyr::mutate(T3 = case_when(
    T3 == "0   (0.00%)" ~ "-",
    TRUE ~ T3)) |>
  dplyr::mutate(T4 = case_when(
    T4 == "0   (0.00%)" ~ "-",
    TRUE ~ T4)) |>
  dplyr::mutate(T5 = case_when(
    T5 == "0   (0.00%)" ~ "-",
    TRUE ~ T5)) |>
  dplyr::mutate(T6 = case_when(
    T6 == "0   (0.00%)" ~ "-",
    TRUE ~ T6)) |>
  dplyr::mutate(T7 = case_when(
    T7 == "0   (0.00%)" ~ "-",
    TRUE ~ T7)) |>
  dplyr::mutate(T8 = case_when(
    T8 == "0   (0.00%)" ~ "-",
    TRUE ~ T8)) |>
  dplyr::mutate(T9 = case_when(
    T9 == "0   (0.00%)" ~ "-",
    TRUE ~ T9)) |>
  dplyr::mutate(T10 = case_when(
    T10 == "0   (0.00%)" ~ "-",
    TRUE ~ T10)) |>
  dplyr::mutate(TL = case_when(
    TL == "0   (0.00%)" ~ "-",
    TRUE ~ TL)) |>
  dplyr::mutate(INDET = case_when(
    INDET == "0   (0.00%)" ~ "-",
    TRUE ~ INDET)) |>
  select(RETOUCHEDPIECETYPOLOGY, T1, T2, T3, T4, T5, T6, T7, T8, T9, T10, TL, INDET, Total) # Ordering values
